Clean data

### 2018-03-30 01_clean-data.Rmd
Use CSVY to be cool

```{r clean-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(here)

@@

saveRDS(results, file.path(here(), "data", "results_clean.rds"))
write_csv(results, file.path(here(), "data", "results_clean.csv"))
```

>>>>

```{r clean-data, warning=FALSE, message=FALSE}
library(tidyverse)
library(here)
library(csvy)

@@

saveRDS(results, file.path(here(), "data", "results_clean.rds"))
write_csvy(results, file = file.path(here(), "data", "results_clean.csv"),
           metadata = file.path(here(), "data", "results_clean.yaml"), na = "NA")
```
